A Method for the Spectroscopic Inference of Stellar Parameters

### 2014-08-22 tex/paper.tex

We opt for the computationally expedient approach that employs a library of model spectra, 
$\flam(\{\vt_{\ast}\}^{\rm grid})$, where $\vt_{\ast} = [T_{\rm eff}, \,\, \log{g}, \,\, 
[{\rm Fe/H}]]$.  However, it is worth noting that the techniques developed here are applicable to 
{\it any} ``front-end" that generates a model spectrum.  In our adopted approach, the model 
spectrum for an arbitrary $\vt_{\ast}$ is interpolated from a spectral library, 
\begin{equation} \label{eqn:interp}
\flam(\{\vt_{\ast}\}^{\rm grid}) \leadsto \flam(\vt_{\ast}),
\end{equation}
where we assign the symbol $\leadsto$ as an interpolation operator.  The multi-dimensional 
interpolation in Eq.~\ref{eqn:interp} needs to be performed many times, so computational efficiency 
is critical.  In practice, a simple tri-linear interpolation is suitably fast, but introduces an 
undesirable level of inaccuracy (particularly in the [Fe/H] dimension).  The interpolation quality 
can be empirically estimated by performing the operation in Eq.~\ref{eqn:interp} across a 
$\{\vt_{\ast}\}^{\rm grid}$ grid point, and then comparing the interpolated spectrum with the 
corresponding library spectrum.  After an extensive exploration of such calculations 
\citep[see also][]{husser12}, we concluded that the best combination of speed and accuracy can be 
achieved by pre-computing a {\it refined} spectral library using a cubic spline interpolation with 
a $\{\vt_{\ast}\}^{\rm grid}$ spacing of [20\,K, 0.1\,dex, 0.1\,dex], and then performing 
tri-linear interpolation over that refined grid.  Overall, this interpolation technique is found to 
be accurate within a few percent per full-resolution model pixel.  Ideally, this pre-interpolation 
could be avoided if the spectral library was computed over a refined grid (with a substantial 
up-front computational investment); but for the time being, we can empirically propagate these 
interpolation uncertainties into the likelihood calculations (as will be described in 
Section~\ref{subsec:likelihood}).  
%% \todo{tests regarding interpolation accuracy}.

@@

Astronomical spectrographs are designed such that the detector over-samples the instrumental 
line-spread function with at least a few pixels.  Therefore, adjacent pixels never record 
completely independent samples of the true spectrum.  In that case, a difference between an 
observed and modeled spectral feature will create a correlated residual that spans multiple 
pixels.  This can be demonstrated practically through the autocorrelation of $\vR$: a slight model 
mismatch will produce correlated residuals over a characteristic scale similar to the instrumental
broadening kernel width ($\sigma_v$).  Figure \ref{fig:class0} highlights a specific example of 
these correlated residuals in real data; a significant autocorrelation signal is found on a $\sim$4 
pixel scale, corresponding to the 3\,km s$^{-1}$ width of $\mathcal{F}_v^{\rm inst}$.

\begin{figure*}[!htb]
\begin{center}
  \includegraphics{correlation_panel.pdf}
  \caption{\textbf{Top}: the big spectrum. \textbf{Left} The same low-amplitude, mildly covariant residuals from Figure~\ref{fig:badlines}, panel 0, but enlarged to show the mildly covariant structure produced by slight mismatch between the data and model spectra.   
  \textbf{Right} The autocorrelation of the residual sequence shown at left. Notice that there is significant correlation for offsets of $\lesssim 4$ pixels.}
\label{fig:class0}
\end{center}
\end{figure*}

@@

For a well-designed spectrograph and sufficiently accurate model, this {\it global} (i.e., present 
throughout the spectrum) covariant structure should have a relatively low amplitude and small 
correlation length.  To describe that structure, we use a stationary covariance kernel (or radial 
basis function) with an amplitude that depends only on the velocity distance between two pixels, 
\begin{equation}
  r_{ij} = r(\lambda_i, \lambda_j) = \Delta v = \frac{c}{2} \left | \frac{\lambda_i 
   - \lambda_j}{ \lambda_i + \lambda_j} \right |,
\end{equation}
where $c$ is the speed of light.  This parametric kernel describes the covariance between pixel 
residuals, 
\begin{equation}
  \Kglobal_{ij} =  \langle \vR_i \; \vR_j \rangle.
  \label{eqn:expectation}
\end{equation}
A variety of kernels have been used in the field of Gaussian processes to parameterize such a 
covariant structure \citep[e.g.,][]{rasmussen05}.  Here, we adopt the commonly-employed \matern\ 
kernel with $\nu = 3/2$,
\begin{equation}
  \Kglobal_{ij}(\vp_{{\mathsf C}, g}) = a_{\rm g} \left(1 + \frac{\sqrt{3}\, r_{ij}}{\ell} \right ) \exp 
   \left (- \frac{\sqrt{3}\, r_{ij}}{\ell} \right ),
   \label{eqn:global}
\end{equation}
where the (hyper-)parameters $\vp_{{\mathsf C}, g} = [a_g, \ell]$ include an amplitude ($a_g$) and 
scale ($\ell$).  To ensure that $\vC$ remains a relatively sparse matrix that 
enables computational expendiency, we employ a Hann window function
\begin{equation}
  w_{ij}^{\rm g} \,(r_0) = \left \{ 
    \begin{array}{cc}
    \frac{1}{2} + \frac{1}{2} \cos \left(\frac{\pi r_{ij}}{r_0} \right) & r_{ij} \le r_0 \\
    0 & r_{ij} > r_0 \\
  \end{array}
  \right .
  \label{eqn:Hann}
\end{equation}
to taper the kernel.  The truncation distance $r_0$ can be fixed to a reasonable multiple of the 
scale (we set $r_0 = 4\ell$).  Figure \ref{fig:matern} demonstrates that random draws from such a 
kernel readily produce correlated structure similar to those seen in a typical residual spectrum.

\begin{figure*}[!htb]
\begin{center}
\includegraphics[width=0.4\textwidth]{figs/matern_matrix.pdf}
\includegraphics[width=0.4\textwidth]{figs/matern_draw.pdf}
\caption{\textbf{Left} Inset zoomed to show a small region of a typical covariance matrix, generated using the kernel in Equation~\ref{eqn:global} and common values for the hyperparameters. There is a small degree of covariance in elements within a few pixels off the diagonal, which quickly tapers off so that the majority of the matrix remains sparse ($\sigma_{ij} = 0$). This matrix is used to model a spectrum which is correlated on a $\sim$few pixel scale.
\textbf{Right} To demonstrate that this matrix properly models the correlated structure of the residuals, we compare the residuals to random residuals generated from a multivariate normal distribution with this covariance matrix. The top panel shows the same residuals shown in Figure~\ref{fig:class0}, and below are plotted three sets of simulated residuals. The amplitude and correlation length of the simulated residuals closely approximates the structure of the actual pixel residuals.}
\label{fig:matern}
\end{center}
\end{figure*}

@@

Assuming that these local residuals are produced primarily by pathological differences in the 
spectral line strength (rather than shape or center), a simple Gaussian is a reasonable residual 
model.  In that case, the $k^{\rm th}$ such local residual could be described as
\begin{equation}
\vR = \frac{a_k}{\sqrt{2\pi}{\sigma_k}} \exp \left[ - \frac{r^2(\lambda,\mu_k)}{2\sigma_k^2} \right],
\end{equation}
with amplitude $a_k$, mean wavelength $\mu_k$, and width $\sigma_k$.  Following 
Eq.~\ref{eqn:expectation}, the covariance of any two pixels related to the $k^{\rm th}$ local 
residual regions can be written
\begin{equation} \label{eqn:kregion}
  \mathcal{K}^{l,k}_{ij} = \frac{a_k^2}{2\pi\sigma_k^2} \exp \left [ - \, \frac{r^2(\lambda_i, \mu_k) + r^2(\lambda_j, \mu_k)}{2 \sigma_k^2}\right ],
\end{equation}
such that the full local covariance kernel composed of a sequence of residual regions is the linear 
combination,
\begin{equation} \label{eqn:klocal}
\Klocal_{ij}(\vp_{{\mathsf C},l}) = \sum_k w^k_{ij} \, \mathcal{K}^{l,k}_{ij},
\end{equation}
with a set of (hyper-)parameters $\vp_{{\mathsf C},l} = [\{a_k, \mu_k, \sigma_k\}]$.  Note that we 
again taper the kernels with Hann windows (Eq.~\ref{eqn:Hann}) to ensure that a sparse covariance 
matrix; in this case, the truncation distance $r_0$ can be set to some multiple of the Gaussian 
width (we use $r_0 = 4\sigma_k$).  Figure \ref{fig:region} shows how this non-stationary Gaussian 
kernel generates a localized region of enhanced variance that successfully mimics the kind of 
residuals produced by an inaccurate spectral line model.  In effect, these kernels down-weight the 
influence of such strong residuals in the likelihood calculation, mitigating any potential bias 
they might induce on inferences of the interesting parameters ($\vT$).  This acts like a robust, 
flexible, and unbiased method for (correlated) outlier rejection that preserves the integrity of 
the probabilistic framework (as opposed to manual or threshold-based clipping or masking).

@@

@@

%\begin{figure*}[!htb]
%\begin{center}
%  \includegraphics[draft, width=2.5in]{figs/stellar_triangle_Kurucz.png}
%  \caption{The posterior probability function of the stellar parameters for WASP-14, an F star, as explored by the MCMC Gibbs sampler. These stellar parameters are marginalized over the Chebyshev ($\cheb$) and noise parameters ($\cov$). Figure generated with \texttt{triangle.py} \citep{foreman-mackey14}.
%}
%\label{fig:stellar_posterior}
%\end{center}
%\end{figure*}

@@

%\begin{figure*}[!htb]
%\begin{center}
%  \includegraphics[draft,width=0.9\textwidth,height=4in]{figs/spectrum_region.pdf}
%  \caption{The spectrum residuals and many random draws from the final covariance matrix showing how the uncertainty in the ``outlier'' lines is identified by the local covariance kernels. Plotted with the increased variance envelope over the residuals.
%}
%\label{fig:regions}
%\end{center}
%\end{figure*}

@@

%\begin{figure*}[!htb]
%\begin{center}
%  \includegraphics{figs/badlines.pdf}
%  \caption{A collection of spectral lines which have imperfect model fits.
%    From left to right: \textbf{Class 0} The majority of spectral lines
%    ($\gtrsim 60$\%) will have minor differences in strength between data and
%    model spectrum, which produce low-amplitude correlations in the residuals
%    on the length scale of the width of a typical spectral line.  \textbf{Class
%    I}: Sometimes ($\lesssim 5$\% of all lines), a missing opacity source in
%    the model (in this case a line-blended \ion{Ca}{2}) leaves a large, highly correlated
%    patch of negative residuals.  \textbf{Class II}: Sometimes ($\lesssim 5$\%
%    of all lines), an extraneous line in the model leaves a large, highly
%    correlated patch of positive residuals.  \textbf{Class III}: If the line strengths are
%    substantially discrepant ($\lesssim 10$\% of all lines), there will be many
%    correlated residuals of moderate amplitude.  The difficulty
%    with class III lines is that for any specific line, there might exist a
%    $\vT$ that will fit the line, but there does not exist a $\vT$ that
%    will properly fit \emph{all} the lines.}
%\label{fig:badlines}
%\end{center}
%\end{figure*}

@@

@@

>>>>

We opt for the computationally expedient approach that employs a library of model spectra, 
$\flam(\{\vt_{\ast}\}^{\rm grid})$, where $\vt_{\ast} = [T_{\rm eff}, \,\, \log{g}, \,\, 
[{\rm Fe/H}]]$.  However, it is worth noting that the techniques developed here are applicable to 
{\it any} ``back-end" that generates a model spectrum.  In our adopted approach, the model 
spectrum for an arbitrary $\vt_{\ast}$ is interpolated from a spectral library, 
\begin{equation} \label{eqn:interp}
\flam(\{\vt_{\ast}\}^{\rm grid}) \leadsto \flam(\vt_{\ast}),
\end{equation}
where we assign the symbol $\leadsto$ as an interpolation operator.  The multi-dimensional 
interpolation in Eq.~\ref{eqn:interp} needs to be performed many times, so computational efficiency 
is critical.  In practice, a simple tri-linear interpolation is suitably fast, but introduces an 
undesirable level of inaccuracy (particularly in the [Fe/H] dimension).  The interpolation quality 
can be empirically estimated by performing the operation in Eq.~\ref{eqn:interp} across a 
$\{\vt_{\ast}\}^{\rm grid}$ grid point, and then comparing the interpolated spectrum with the 
corresponding library spectrum.  After an extensive exploration of such calculations 
\citep[see also][]{husser12}, we concluded that this interpolation
technique is found to be accurate within a few percent per full-resolution
model pixel and $\lesssim 1$\% once the spectrum is downsampled to the pixels of the detector. Ideally,
this pre-interpolation could be avoided if the spectral library was computed
over a refined grid (with a substantial up-front computational investment); but
for the time being, we can empirically propagate these interpolation
uncertainties into the likelihood calculations (as will be described in 
Section~\ref{subsec:likelihood}).  
%% \todo{tests regarding interpolation accuracy}.

@@

Astronomical spectrographs are designed such that the detector over-samples the instrumental 
line-spread function with at least a few pixels.  Therefore, adjacent pixels never record 
completely independent samples of the true spectrum.  In that case, a difference between an 
observed and modeled spectral feature will create a correlated residual that spans multiple 
pixels.  This can be demonstrated practically through the autocorrelation of $\vR$: a slight model 
mismatch will produce correlated residuals over a characteristic scale similar to the instrumental
broadening kernel width ($\sigma_v$).  Figure \ref{fig:class0} highlights a specific example of 
these correlated residuals in real data; a significant autocorrelation signal is found on a $\sim$5 
pixel scale, corresponding to the 6.8\,km s$^{-1}$ FWHM of $\mathcal{F}_v^{\rm inst}$.

\begin{figure}[!htb]
\begin{center}
  \includegraphics{residuals_23.pdf}
  \includegraphics{class0_residuals.pdf}
  \includegraphics{class0_autocorrelation.pdf}
  \caption{\textbf{Top}: A typical model fit to a data spectrum, with
  parameters drawn from the posterior distribution, and the residuals that
  result. \textbf{Left} The low-amplitude, mildly covariant residuals enlarged
  to show the mildly covariant structure produced by slight mismatch between
  the data and model spectra.   \textbf{Right} The autocorrelation of the
residual sequence shown at left. Notice that there is significant correlation
for offsets of $\lesssim 5$ pixels.}
\label{fig:class0}
\end{center}
\end{figure}

@@

For a well-designed spectrograph and sufficiently accurate model, this {\it global} (i.e., present 
throughout the spectrum) covariant structure should have a relatively low amplitude and small 
correlation length.  To describe that structure, we use a stationary covariance kernel (or radial 
basis function) with an amplitude that depends only on the velocity distance between two pixels, 
\begin{equation}
  r_{ij} = r(\lambda_i, \lambda_j) = \Delta v = \frac{c}{2} \left | \frac{\lambda_i 
   - \lambda_j}{ \lambda_i + \lambda_j} \right |,
\end{equation}
where $c$ is the speed of light.  This parametric kernel describes the covariance between pixel 
residuals, 
\begin{equation}
  \Kglobal_{ij} =  \langle \vR_i \; \vR_j \rangle.
  \label{eqn:expectation}
\end{equation}
A variety of kernels have been used in the field of Gaussian processes to parameterize such a 
covariant structure \citep[e.g.,][]{rasmussen05}.  Here, we adopt the commonly-employed \matern\ 
kernel with $\nu = 3/2$,
\begin{equation}
  \Kglobal_{ij}(\vp_{{\mathsf C}, g}) = a_{\rm g} \left(1 + \frac{\sqrt{3}\, r_{ij}}{\ell} \right ) \exp 
   \left (- \frac{\sqrt{3}\, r_{ij}}{\ell} \right ),
   \label{eqn:global}
\end{equation}
where the (hyper-)parameters $\vp_{{\mathsf C}, g} = [a_g, \ell]$ include an amplitude ($a_g$) and 
scale ($\ell$).  To ensure that $\vC$ remains a relatively sparse matrix that 
enables computational expendiency, we employ a Hann window function
\begin{equation}
  w_{ij}^{\rm g} \,(r_0) = \left \{ 
    \begin{array}{cc}
    \frac{1}{2} + \frac{1}{2} \cos \left(\frac{\pi r_{ij}}{r_0} \right) & r_{ij} \le r_0 \\
    0 & r_{ij} > r_0 \\
  \end{array}
  \right .
  \label{eqn:Hann}
\end{equation}
to taper the kernel.  The truncation distance $r_0$ can be fixed to a reasonable multiple of the 
scale (we set $r_0 = 4\ell$).  Figure \ref{fig:matrix} demonstrates that random draws from such a 
kernel readily produce correlated structure similar to those seen in a typical residual spectrum.

\begin{figure*}[!htb]
\begin{center}
\includegraphics{figs/matrix_compilation.pdf}
\caption{\textbf{Top}: A typical model fit and residual spectrum with a demonstrative region shaded in grey, showing the scale and structure of the residuals. \textbf{Left column}: A small inset of the covariance matrix corresponding to the gray region. Note that the colorbar scale changes with each inset in order to best illustrate the structure of the matrix. \textbf{Right column}: Each panel shows three random draws (gray) from a multivariate normal distribution using the covariance matrix in the left column. At the bottom of each panel are the one, two, and three sigma contours (orange) of 200 random draws overlaid with the actual residuals from the gray region. \textbf{First row}: White, Poisson-only noise ($\delta_{ij}\sigma_i$) does a poor job of reproducing both the scale and structure of a typical residual spectrum. \textbf{Second row}: The addition of a global kernel ($\mathcal{K}^{\rm g}$) yields random draws that closely approximate the structure and amplitude of the residuals, but miss the strong outlier line at 5202.2 \AA. \textbf{Third row}: Finally, adding in a local kernel ($\mathcal{K}^l$) at the location of the outlier produces random draws that completely match the structure of the residuals. Interestingly, note that the covariance matrix can produce random draws that have negative, positive, and even flat residual lines. The point is that with a non-trivial covariance matrix, the likelihood function can now accommodate the residuals generated from a typical spectroscopic fit. Stated differently, random draws from the likelihood function can now produce behavior that looks like the residuals, whereas before with only white noise it could not. All parameters of the covariance kernels are determined self-consistently along with the stellar parameters. }
\label{fig:matrix}
\end{center}
\end{figure*}

@@

Assuming that these local residuals are produced primarily by pathological differences in the 
spectral line strength (rather than shape or center), a simple Gaussian is a reasonable residual 
model.  In that case, the $k^{\rm th}$ such local residual could be described as
\begin{equation}
\vR = a_k \exp \left[ - \frac{r^2(\lambda,\mu_k)}{2\sigma_k^2} \right],
\end{equation}
with peak amplitude $a_k$, mean wavelength $\mu_k$, and width $\sigma_k$.  Following 
Eq.~\ref{eqn:expectation}, the covariance of any two pixels related to the $k^{\rm th}$ local 
residual regions can be written
\begin{equation} \label{eqn:kregion}
  \mathcal{K}^{l,k}_{ij} = a_k^2 \exp \left [ - \, \frac{r^2(\lambda_i, \mu_k) + r^2(\lambda_j, \mu_k)}{2 \sigma_k^2}\right ],
\end{equation}
such that the full local covariance kernel composed of a sequence of residual regions is the linear 
combination,
\begin{equation} \label{eqn:klocal}
\Klocal_{ij}(\vp_{{\mathsf C},l}) = \sum_k w^k_{ij} \, \mathcal{K}^{l,k}_{ij},
\end{equation}
with a set of (hyper-)parameters $\vp_{{\mathsf C},l} = [\{a_k, \mu_k, \sigma_k\}]$.  Note that we 
again taper the kernels with Hann windows (Eq.~\ref{eqn:Hann}) to ensure a sparse covariance 
matrix; in this case, the truncation distance $r_0$ can be set to some multiple of the Gaussian 
width (we use $r_0 = 4\sigma_k$).  Figure \ref{fig:matrix} shows how this non-stationary Gaussian 
kernel generates a localized region of enhanced variance that successfully mimics the kind of 
residuals produced by an inaccurate spectral line model.  In effect, these kernels down-weight the 
influence of such strong residuals in the likelihood calculation, mitigating any potential bias 
they might induce on inferences of the interesting parameters ($\vT$).  This acts like a robust, 
flexible, and unbiased method for (correlated) outlier rejection that preserves the integrity of 
the probabilistic framework (as opposed to manual or threshold-based clipping or masking).

@@

\begin{figure*}[!htb]
\begin{center}
\includegraphics{figs/residuals_Kurucz_logg.pdf}
\caption{Kurucz WASP-14. One, two, and three sigma contours formed from 200 random draws from the covariance matrix.}
\label{fig:residuals_Kurucz}
\end{center}
\end{figure*}

\begin{figure}[!htb]
\begin{center}
  \includegraphics[width=0.5\textwidth]{figs/Kurucz_triangle.pdf}
  \caption{The posterior probability function of the stellar parameters for WASP-14, an F star, as explored by the MCMC Gibbs sampler. These stellar parameters are marginalized over the Chebyshev ($\cheb$) and noise parameters ($\cov$). Figure generated with \texttt{triangle.py} \citep{foreman-mackey14}.
}
\label{fig:stellar_posterior}
\end{center}
\end{figure}

\begin{deluxetable}{lr@{$\pm$}l} 
\tablecaption{\label{table:Kurucz}WASP-14 {\sc CfA/Kurucz} results}
\tablehead{\colhead{Parameter} & \multicolumn{2}{c}{Value}}
\startdata
\cutinhead{Stellar parameters}
$T_{\rm eff}$ & 6517.1 & 12.5 K \\
$\log_{10} g$ & \multicolumn{2}{c}{4.29 dex} \\
$\Z$ & -0.27 & 0.01 dex \\
$v \sin i$ & 4.29 & 0.05 $\kms$\\
$v_z$ & -4.620 & 0.016 $\kms$ \\
$\log_{10} \Omega$ & -12.7181 & 0.0004 \\
\cutinhead{Order 22 nuisance parameters}
$\log_{10} \cc{22}{0}$ &  0.0085 & 0.0005\\
$\cc{22}{1}$ & -0.0142 & 0.0015\\
$\cc{22}{2}$ & -0.0145 & 0.0017\\
$\cc{22}{3}$ & -0.0031 & 0.0011\\
\\
$b_{22}$ & 1.04 & 0.02 \\
$\log_{10} a_{{\rm g}, 22}$ & -14.63 & 0.020 $\textrm{erg}\;\textrm{cm}^{-2}\;\textrm{s}^{-1}\;\textrm{\AA}^{-1}$\\
$l_{22}$ & 7.54 & 0.77 $\kms$ \\

\cutinhead{Order 23 nuisance parameters}
$\log_{10} \cc{23}{0}$ & 0.0030 & 0.0006 \\
$\cc{23}{1}$ & -0.0133 & 0.0016 \\
$\cc{23}{2}$ & -0.0247 & 0.0014 \\
$\cc{23}{3}$ &  0.0012 &  0.0013\\
\\
$b_{23}$ & 1.01 & 0.02 \\
$\log_{10} a_{{\rm g}, 23}$ & -14.55 & 0.015 $\textrm{erg}\;\textrm{cm}^{-2}\;\textrm{s}^{-1}\;\textrm{\AA}^{-1}$\\
$l_{23}$ & 6.52 & 0.50 \\

\cutinhead{Order 24 nuisance parameters}
$\log_{10} \cc{24}{0}$ & \multicolumn{2}{c}{0.00} \\
$\cc{24}{1}$ & -0.0103 & 0.0016 \\
$\cc{24}{2}$ & -0.0112 & 0.0013\\
$\cc{24}{3}$ &  0.0002 & 0.0012\\
\\
$b_{24}$ & 1.02 & 0.02 \\
$\log_{10} a_{{\rm g}, 24}$ & -14.61 & 0.02 $\textrm{erg}\;\textrm{cm}^{-2}\;\textrm{s}^{-1}\;\textrm{\AA}^{-1}$\\
$l_{24}$ & 7.33 & 0.59 $\kms$ \\
\enddata
\end{deluxetable}

\begin{figure}[!htb]
\begin{center}
\includegraphics{figs/metacomparison.pdf}
\caption{Comparing all the posteriors.}
\label{fig:metacomparison}
\end{center}
\end{figure}

@@

@@

@@

\begin{figure}[!htb]
\begin{center}
  \includegraphics{figs/badlines0.pdf}
  \includegraphics{figs/badlines1.pdf}
  \includegraphics{figs/badlines2.pdf}
  \includegraphics{figs/badlines3.pdf}
  \caption{A collection of spectral lines which have imperfect model fits.
    \textbf{First panel} The majority of spectral lines ($\gtrsim 60$\%) will
    have minor differences in strength between data and model spectrum, which
    produce low-amplitude correlations in the residuals on the length scale of
    the width of a typical spectral line.  \textbf{Second panel}: Sometimes
    ($\lesssim 5$\% of all lines), a missing opacity source in the model (in
    this case a line-blended \ion{Ca}{2}) leaves a large, highly correlated
    patch of negative residuals.  \textbf{Third panel}: Sometimes ($\lesssim
    5$\% of all lines), an extraneous line in the model leaves a large, highly
    correlated patch of positive residuals. \textbf{Fourth panel}: If the line
    strengths are substantially discrepant ($\lesssim 10$\% of all lines),
    there will be many correlated residuals of moderate amplitude.  The
    difficulty with class III lines is that for any specific line, there might
    exist a $\vT$ that will fit the line, but there does not exist a $\vT$ that
    will properly fit \emph{all} the lines.}
\label{fig:badlines}
\end{center}
\end{figure}

@@

\section{Tables}

\begin{deluxetable}{ll}
\tablecaption{Nomenclature used in this document}
\tablehead{
  \colhead{Symbol} & \colhead{Description}
}
\startdata
$\lambda_i$ & wavelength corresponding to a given pixel $i$\\
$\vt_{\ast}$ & fundamental stellar parameters, $T_{\rm eff}, \log(g), \Z, \A$\\
$\{\vt_{\ast}\}^{\rm grid}$ & stellar parameters that specify a spectrum from a synthetic library\\
$\vt_{\rm obs}$ & stellar parameters $v \sin i$, $v_z$, $A_V$, and $R^2/d^2$ that\\
  & are applied during ``post processing'' of the synthetic spectrum\\
$\vt$ & $\{\vt_{\ast},\vt_{\rm obs}\}$, all stellar parameters\\

@@

\appendix
